Supplementary appendix

### 2019-06-28 paper3_APPENDIX_revision_01.Rmd
Add files via upload

```{r , include=FALSE, echo=FALSE}
source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

@@

# 3. Summary statistics

@@

# 4. Supplementary analyses

@@

# 5. English translation of the survey experiment

>>>>

```{r , include=FALSE, echo=FALSE}
#load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")

source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

@@

# 3. Power estimations

In this section, I report the results of power estimations, which I conducted after collecting and analyzing the data. I have conducted seperate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions bewteen areas and the manipulations; and (4) Two-way interactions bewteen the relevance manipulation and the manipulations (in the Haifa-Bay area).

These power estimations were conducted in R software, through regression models simulations with 1,000 interations for each effect size [code adopted from @hughes_website_2017]. All these tests refer to a *p-value* of .05 (one-tailed), with `set.seed(2018)`. These analyses refer to a the analytical sample size (*N* = `r nrow(SVIVA2_01)`, *N*<sub>*Haifa-Bay*</sub>=`r nrow(SVIVA2_01_haifa)`, *N*<sub>*Center*</sub>=`r nrow(SVIVA2_01_center)`). Finally, I assumed that the error term is normally distributed (Mean = 0, SD = 1).

**Figure XX: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}

results.main %>%
    group_by(main.effect,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

ggplot(aes(x=effect_sizes, y=power,color = main.effect)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
  scale_x_continuous(name = "Main effect (SDs)",limits = c(0.05,0.3),breaks = seq(0,0.3,0.05))+
  scale_colour_manual(name = "Manipulation",
                      values = c("dodgerblue3","orange2"),
                      labels = c("Information", "Symbols"))+
  theme_bw()
```

**Figure XX: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.conditional %>%
    group_by(cond.effect,
             area,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

ggplot(aes(x=effect_sizes, y=power,color = cond.effect)) +
    geom_point() +
    geom_line() +
  facet_grid(cols = vars(area)) +
    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
  scale_x_continuous(name = "Conditional effect (SDs)",limits = c(0.05,0.3),breaks = seq(0,0.3,0.05))+
  scale_colour_manual(name = "Manipulation",
                      values = c("dodgerblue3","orange2"),
                      labels = c("Information", "Symbols"))+
theme_bw()
```

**Figure XX: Power of Interactions with area**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.area %>%
    group_by(Interaction,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

ggplot(aes(x=effect_sizes, y=power,color = Interaction)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
  scale_x_continuous(name = "Interaction coefficient (SDs)",limits = c(0.1,0.5),breaks = seq(0,0.5,0.1))+
    scale_colour_manual(name = "Interaction",
                      values = c("dodgerblue3","orange2"),
                      labels = c("Information", "Symbols"))+
  theme_bw()
```

**Figure XX: Power of Interactions with relevance manipulation**

```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.relevance %>%
    group_by(Interaction,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>% 
 ggplot(aes(x=effect_sizes, y=power,color = Interaction)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
    scale_x_continuous(name = "Interaction coefficient (SDs)",limits = c(0.1,0.5),breaks = seq(0,0.5,0.1))+
    scale_colour_manual(name = "Interaction",
                      values = c("dodgerblue3","orange2"),
                      labels = c("Information", "Symbols"))+
  theme_bw()
```

# 4. Summary statistics

@@

# X raw experimental results

```{r}
t3.comb <- rbind(t3.haifa,
                 t3.center) %>%
  filter(str_detect(variable,"policy")==T) %>%
  select(-starts_with("statistic")) %>%

  mutate(AREA_Center = rep(c("Haifa-Bay","Center"),each=2)) %>% 
  arrange(desc(AREA_Center)) %>% 
  select(AREA_Center,1:11)

```{r, echo=FALSE, warning=FALSE, message=F}

#labels of vars
vars.lab = c(
         "Gender (Woman=1)",
         "Age",
         "Trust in government ministries",
         "Political Ideology (10 = extreme left)",
         "Education",
         "Income (5=high)",
         "Parents",
         "Parents of young children (under 12)",
         "Interest in environmental issues",
         "Air-pollution policy",
         "Recycling policy"
)

vars <- c(var1 = "GENDER", 
          var2 ="AGE",
          var3 ="GOV_TRUST",
          var4 = "IDEOLOGY", 
          var5 ="EDUCATION",
          var6 ="INCOME",
          var7 = "CHILDREN", 
          var8 ="CHILDREN_young",
          var9 ="ENVIRONMENT_INTEREST",
          var91 ="TRUST_air_INDEX",
          var92 ="TRUST_waste_INDEX")

t11.all <- SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX) %>% 
  gather(key = variable, value = value) %>% 
  group_by(variable) %>% 
  summarise(mean.var = mean(value,na.rm = T) %>% round(3),
            sd.var = sd(value,na.rm = T) %>% round(3)) %>% 
  mutate(all = str_c(mean.var, " (",sd.var,")")) %>% 
  as.data.frame() %>% 
  select(-mean.var,-sd.var)

t11.symbol <- SVIVA2_01 %>%
  mutate(symbols.t = Recode(SYMBOL,"0='no';1='fake';2='real'")) %>% 
  select(symbols.t,
         TRUST_air_INDEX,
         TRUST_waste_INDEX) %>%
  gather(key = variable, value = value, -symbols.t) %>% 
  group_by(symbols.t, variable) %>% 
  summarise(value = list(value)) %>% 
  spread(symbols.t, value) %>% 
  group_by(variable) %>%

  mutate(mean_no = round(mean(unlist(no),na.rm = T),3),
         mean_fake = round(mean(unlist(fake),na.rm = T),3),
         mean_real = round(mean(unlist(real),na.rm = T),3),
         sd_no = round(sd(unlist(no),na.rm = T),3),
         sd_fake = round(sd(unlist(fake),na.rm = T),3),
         sd_real = round(sd(unlist(real),na.rm = T),3)) %>%
  mutate(no = str_c(mean_no, " (",sd_no,")"),
         fake = str_c(mean_fake, " (",sd_fake,")"),
         real = str_c(mean_real, " (",sd_real,")")) %>% 
  select(variable,
         no,
         fake,
         real) %>% 
  as.data.frame()

t11.info <- SVIVA2_01 %>% 
  mutate(info.t = ifelse(INFORMATION_air==1,"air_strong","air_weak")) %>% 
  select(info.t,
         TRUST_air_INDEX,
         TRUST_waste_INDEX) %>%
  gather(key = variable, value = value, -info.t) %>% 
  group_by(info.t, variable) %>% 
  summarise(value = list(value)) %>% 
  spread(info.t, value) %>% 
  group_by(variable) %>%

  mutate(mean_strong = round(mean(unlist(air_strong),na.rm = T),3),
         mean_weak = round(mean(unlist(air_weak),na.rm = T),3),
         sd_strong = round(sd(unlist(air_strong),na.rm = T),3),
         sd_weak = round(sd(unlist(air_weak),na.rm = T),3),
         t_value.info = round(t.test(unlist(air_strong), unlist(air_weak))$statistic,3)) %>% 
  mutate(air_strong = str_c(mean_strong, " (",sd_strong,")"),
         air_weak = str_c(mean_weak, " (",sd_weak,")")) %>% 
  select(variable,
         air_strong,
         air_weak) %>% 
  as.data.frame() %>% 
  arrange(variable)

t11.relevance <- SVIVA2_01 %>%
  mutate(relevance.t = ifelse(RELEVANCE_exp==1,"treatment","control")) %>% 
  select(relevance.t,
         TRUST_air_INDEX,
         TRUST_waste_INDEX) %>%
  gather(key = variable, value = value, -relevance.t) %>% 
  group_by(relevance.t, variable) %>% 
  summarise(value = list(value)) %>% 
  spread(relevance.t, value) %>% 
  group_by(variable) %>%

  mutate(mean_treatment = round(mean(unlist(treatment),na.rm = T),3),
         mean_control = round(mean(unlist(control),na.rm = T),3),
         sd_treatment = round(sd(unlist(treatment),na.rm = T),3),
         sd_control = round(sd(unlist(control),na.rm = T),3),
         t_value.relevance = round(t.test(unlist(treatment), unlist(control))$statistic,3)) %>% 
  mutate(treatment = str_c(mean_treatment, " (",sd_treatment,")"),
         control = str_c(mean_control, " (",sd_control,")")) %>% 
  select(variable,
         treatment,
         control) %>% 
  as.data.frame() %>% 
  arrange(variable)

t11.comb <- t11.all %>% 
  cbind(t11.symbol  %>% 
          select(-variable)) %>% 
  cbind(t11.info %>% 
          select(-variable)) %>%
  cbind(t1.relevance %>% 
          select(-variable)) %>% 
  mutate(variable = c("Air-pollution policy","Recycling policy"))

t13.haifa <- t3.haifa %>% 
  filter(str_detect(variable,"policy")==T) %>%
  select(-starts_with("statistic"),
         -starts_with("t_"))

t13.center <- t3.center %>% 
  filter(str_detect(variable,"policy")==T) %>%
  select(-starts_with("statistic"),
         -starts_with("t_"))

t11.all <- rbind(
  t11.comb,
  t13.haifa,
  t13.center
) %>% 
  mutate(area = rep(c("All","Haifa-Bay","Center"),each=2)) %>% 
  select(area,1:9)

```{r}
t11.all %>% 
  kable(col.names = c("Area",
                      "Policy",
                    "All sample",
                    "No symbols",
                    "Fake symbols",
                    "Real symbols",
                    "Strong Air-pollution (Weak recycling)",
                    "Weak air-pollution (Strong recycling)",
                    "Treatment",
                    "Control"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  add_header_above(c(" " = 3, 
                     "Symbols groups" = 3,  
                     "Information groups" = 2, 
                     "Relevance groups" = 2))  %>%
  collapse_rows(columns = 1, valign = "top")
```

# 5. Supplementary analyses

@@

# 6. English translation of the survey experiment
